Pteropod biomarker analysis

### 2018-03-01 eval.Rmd
new env vars, biomark ratio

data(envdat)
data(biodat)
```

@@

env <- select(dat_frm, Ara, O2, pCO2, Sal, TA, Temp)
bio <- select(dat_frm, CAT, GR, GSHonGSSG, GST, LPX, ORAC, SOD)

@@

# pearson, spearman correlation between biomarkers and env variables
cr <- dat_frm %>%
  gather('env_lab', 'env_val', Ara, O2, pCO2, Sal, TA, Temp) %>% 
  gather('bio_lab', 'bio_val', CAT, GR, GSHonGSSG, GST, LPX, ORAC, SOD) %>% 
  group_by(env_lab, bio_lab) %>% 
  summarise(
    sp_cr = round(cor.test(env_val, bio_val, method = 'spearman')$estimate, 2),
    sp_pv = p_ast(cor.test(env_val, bio_val, method = 'spearman')$p.value),
    pr_cr = round(cor.test(env_val, bio_val, method = 'pearson')$estimate, 2),
    pr_pv = p_ast(cor.test(env_val, bio_val, method = 'pearson')$p.value)
  ) %>% 
  unite('sp_cr', sp_cr, sp_pv, sep = ' ') %>% 
  unite('pr_cr', pr_cr, pr_pv, sep = ' ')

@@

>>>>

data(envdat)
data(biodat)

envchr <- c('Ara', 'O2', 'pH', 'Fluor', 'CO3', 'pCO2', 'Sal', 'TA', 'Temp', 'Latitude')
biochr <- c('CAT', 'GR', 'GSHonGSSG', 'GST', 'LPX', 'ORAC', 'SOD', 'ORACvLPX')
```

@@

env <- select(dat_frm, one_of(envchr))
bio <- select(dat_frm, one_of(biochr))

@@

# pearson, spearman correlation between biomarkers and env variables
cr <- dat_frm %>%
  gather('env_lab', 'env_val', one_of(envchr)) %>% 
  gather('bio_lab', 'bio_val', one_of(biochr)) %>% 
  group_by(env_lab, bio_lab) %>% 
  summarise(
    sp_cr = round(cor.test(env_val, bio_val, method = 'spearman')$estimate, 2),
    sp_pv = p_ast(cor.test(env_val, bio_val, method = 'spearman')$p.value),
    pr_cr = round(cor.test(env_val, bio_val, method = 'pearson')$estimate, 2),
    pr_pv = p_ast(cor.test(env_val, bio_val, method = 'pearson')$p.value)
  ) %>% 
  unite('sp_cr', sp_cr, sp_pv, sep = ' ') %>% 
  unite('pr_cr', pr_cr, pr_pv, sep = ' ')

@@

## ORACvLPX
```{r}
knitr::kable(filter(mods, bio_lab %in% 'ORACvLPX')$data[[1]], caption = 'ORACvLPX')
```
